### 2014-04-16 doc/uist14/relatedwork.tex
doing vfill and eject also make sure titles are captical cases in related works

\subsection{Pointing in physical spaces}
Rukzio studied alternative methods for selecting devices in physical spaces and found that users strongly preferred either tapping target appliances with a mobile device or pointing at a distance to browsing a list~\cite{rukzio_experimental_2006}.

>>>>

\subsection{Pointing in Physical Spaces}
Rukzio studied alternative methods for selecting devices in physical spaces and found that users strongly preferred either tapping target appliances with a mobile device or pointing at a distance to browsing a list~\cite{rukzio_experimental_2006}.
